Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-28 manuscript/supplementaryRW.Rmd
small last changes in supplementary materials

-   Bugmann, H. (1994). On the ecology of mountainous forests in a
    changing climate: A simulation study. Huber, N., Bugmann, H., &
    Lafond, V. (2020). Capturing ecological processes in dynamic forest
    models: Why there is no silver bullet to cope with complexity.
    Ecosphere, 11(5). <https://doi.org/10.1002/ecs2.3109>

@@

The most complete reference resource for the SIBYLA model and
regeneration module is:

@@

@@

```{r diff, echo=FALSE, fig.cap="Departure of each model in the representation of the main species recruitment relative abundance from the observations across the environmental gradients for a 10cm treshold. The values shown are the mean of samples per site and across sites in bins, where the range of the climatic water balance (cm) and seasonal degree-day sum (dºC) was divided in 10 bins. The point sizes represent ratio between recruited basal area of the species and the total recruited basal area for all the species. The color gradient shows the difference between the simulated and observed ratio between recruited basal area of the species and the total recruited basal area: grey cell represent areas of the envirnomental gradient in which the model had R BA share  and the empirical dara did not becuase both recruitment and stand level recruitments were equalt to zero.", out.width='100%',out.height= "80%", fig.pos='H'}
knitr::include_graphics(here::here("figures", "HeatEnvGrad_10circles_10.png"))
```

## References

>>>>

-   Bugmann, H. (1994). On the ecology of mountainous forests in a
    changing climate: A simulation study.
-   Huber, N., Bugmann, H., & Lafond, V. (2020). Capturing ecological
    processes in dynamic forest models: Why there is no silver bullet to
    cope with complexity. Ecosphere, 11(5).
    <https://doi.org/10.1002/ecs2.3109>

@@

The most complete reference resource for the SIBYLA model and
regeneration module are:

@@

The most complete reference resource for the SIBYLA model and
regeneration module are:

@@

```{r diff, echo=FALSE, fig.cap="Departure of each model in the representation of the main species recruitment relative abundance from the observations across the environmental gradients for a 10cm treshold. The values shown are the mean of samples per site and across sites in bins, where the range of the climatic water balance (cm) and seasonal degree-day sum (dºC) was divided in 10 bins. The point sizes represent ratio between recruited basal area of the species and the total recruited basal area for all the species. The color gradient shows the difference between the simulated and observed ratio between recruited basal area of the species and the total recruited basal area: grey cell represent areas of the envirnomental gradient in which the model had R BA share  and the empirical dara did not becuase both recruitment and stand level recruitments were equal to zero.", out.width='100%',out.height= "80%", fig.pos='H'}
knitr::include_graphics(here::here("figures", "HeatEnvGrad_10circles_10.png"))
```
